% !TEX root = ../main.tex
% This is a sample file for an abstract submission.
% Author: Indrajit Ghosh
% Created On: Dec 19, 2024
%
% For each abstract submitted by the speakers, create a separate .tex file like this one.
% Then, include these abstract files into the main.tex document.
%
\subsection*{Algebraic Aspects and Functoriality of the Set of Affiliated Operators} % CHANGE_HERE
\noindent
\textbf{Speaker:} Indrajit Ghosh \\ % CHANGE_HERE
\textbf{Affiliation:} SRF, Stat-Math Unit, ISI Bangalore \\ % CHANGE_HERE

\noindent\textbf{Abstract.}
In their foundational work, Murray and von Neumann studied a specific class of unbounded operators that are, in a precise sense, associated with a given von Neumann algebra. These operators are now referred to as \emph{Murray-von Neumann affiliated operators}. Their study led to significant structural results concerning the underlying von Neumann algebra. It was later proven that for \emph{finite} von Neumann algebras, the set of affiliated operators, as defined by Murray and von Neumann, forms a well-structured algebraic object, specifically a topological $*$-algebra. However, the algebraic structure of affiliated operators in the general case remains mysterious. In this talk, we introduce a new class of unbounded operators associated with a given von Neumann algebra, which we term \textit{affiliated operators}. We show that for a von Neumann algebra $\mathscr{M}$, the set of affiliated operators, denoted $\mathscr{M}_{\textrm{aff}}$, is closed under the operator sum, product, Kaufman inverse, and adjoint operations. Furthermore, we demonstrate that $\mathscr{M}_{\textrm{aff}}$ has the structure of a \textit{(right) near-semiring}. Additionally, we prove that the near-semiring $\mathscr{M}_{\textrm{aff}}$ transforms \textit{functorially} under normal $*$-homomorphisms, establishing it as an intrinsic construction of $\mathscr{M}$. As a key result, we show that this new notion of affiliation encompasses the classical Murray-von Neumann affiliation. By leveraging the functoriality of $\mathscr{M}_{\textrm{aff}}$, we also demonstrate that the set of Murray-von Neumann affiliated operators is intrinsic to $\mathscr{M}$, thus independent of any specific representation.


